{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Started correction of GPM slides

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenario in high-density NBH heated plasma on TCV has been established
}
\end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> AUG: Neutrals at lower current are substantially
          higher even with similar edge density profiles.
        \item<7|only@7> AUG: Similarly to the observation at constant
          q$_{95}$ target peak density rollover and radiation movement
          from the target occurs earlier in density at lower plasma current
      \item<8|only@8> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<9|only@9> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<10|only@10> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<11|only@11> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

>>>>

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenario in high-density NBH heated plasma on TCV has been established
}
\end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection
        length. \alert{L$_{\parallel} at TCV is almost one order of
          magnitude larger than AUG$}
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> AUG: Neutrals at lower current are substantially
          higher even with similar edge density profiles.
        \item<7|only@7> AUG: Similarly to the observation at constant
          q$_{95}$ target peak density rollover and radiation movement
          from the target occurs earlier in density at lower plasma current
      \item<8|only@8> TCV: This tendency is substantially confirmed at
        TCV even though larger scatter in the data has been
        obtained. To be combined with similar experiment performed
        under MST1-2015  
      \item<9|only@9> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<10|only@10> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<11|only@11> TCV: Even at TCV no big differences in blob
        size has been observed. Statistics should be increased
        including past experiment from MST1-2015 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
